Formulating and Validating RDF Constraints Generically

### 2015-03-06 paper/paper 2/paper 2.tex
formatting

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & Book & identifier & - & ISBN & $\forall$ & - \\
      class & ISBN & - & - & xsd:string & regex & '\string^\d{9}[\d|X]\$' \\
		\end{tabular}
	\caption{Simple Constraint (Not Expressible in DL)}
	\label{tab:simple-constraint-not-expressible-in-dl)}
\end{table} \tb{Erman, can you please format the regular expression in the table above correctly?}
The \emph{literal pattern matching} constraint introduces the new \emph{constraining element} \emph{regex}.
For this new \emph{constraining element}, the validation must be implemented.
This has to be done once for each \emph{generic constraint type} which cannot be expressed in DL.

>>>>

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & Book & identifier & - & ISBN & $\forall$ & - \\
      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
		\end{tabular}
	\caption{Simple Constraint (Not Expressible in DL)}
	\label{tab:simple-constraint-not-expressible-in-dl)}
\end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
The \emph{literal pattern matching} constraint introduces the new \emph{constraining element} \emph{regex}.
For this new \emph{constraining element}, the validation must be implemented.
This has to be done once for each \emph{generic constraint type} which cannot be expressed in DL.
